Estimating epidemiological quantities from repeated cross-sectional prevalence measurements

### 2022-03-06 docs/paper.Rmd
read data read in

params_table <- here::here("outputs", "example-parameters.csv")
if (!file.exists(params_table)) {
  source(here::here("scripts", "simple-example.R"))
}
params <- fread(params_table)
params[name == "gamma", name := ifelse(index == 1, "gamma (infection)", "gamma (vaccination)")]
params[, Description := fcase(
           name == "beta", "Proportion infected that seroconvert",
           name == "gamma (infection)", "Antibody waning following infection (daily rate)",
           name == "gamma (vaccination)", "Antibody waning following vaccination (daily rate)",
           name == "delta", "Proportion vaccinated that seroconvert",
           name == "k", "Efficacy adjustment of immunity following infection",
           name == "l", "Efficacy adjustment of immunity following vaccination")]
biol_params <- params[!is.na(Description)]
biol_params[, `Estimate (90% CI)` := paste0(signif(q50, 2), " (", signif(q5, 2), "--", signif(q95, 2), ")")]
biol_params <- biol_params[, list(Parameter = name,
                                  Description,
                                  `Estimate (90% CI)`)]

>>>>

params_table <- here::here("outputs", "example-parameters.csv")
if (!file.exists(params_table)) {
  source(here::here("scripts", "simple-example.R"))
}
params <- fread(params_table)
params[name == "gamma",
       name := ifelse(index == 1, "gamma (infection)", "gamma (vaccination)")
]
params[,
  Description := fcase(
    name == "beta", "Proportion infected that seroconvert",
    name == "gamma (infection)", "Antibody waning following infection (daily rate)",
    name == "gamma (vaccination)", "Antibody waning following vaccination (daily rate)",
    name == "delta", "Proportion vaccinated that seroconvert",
    name == "k", "Efficacy adjustment of immunity following infection",
    name == "l", "Efficacy adjustment of immunity following vaccination")
]
biol_params <- params[!is.na(Description)]
biol_params[, 
  `Estimate (90% CI)` := paste0(
    signif(q50, 2), " (", signif(q5, 2), "--", signif(q95, 2), ")"
  )
]
biol_params <- biol_params[,
  .(Parameter = name, Description, `Estimate (90% CI)`)
]
